A systematic search for transiting planets using \KT

### 2015-02-07 ms.tex
Facilities tag in acknowledgements
more fixes
A few edits

The methods developed within this paper are highly relevant to the upcoming 
\tess\ mission (Cite-Ricker 14). 
\tess will feature pointing precision of \sim 3 arcseconds (cite), 
similar to the level of pointing drift with \KT.
Moreover, the typical star will be only observed for one month at a time, and
the typical transit detection will be at a similar signal-to-noise ratio as
with \KT.

@@

The starting point for analysis is the raw pixel data.
We download the full set of XXX target pixel files for \KT's Campaign 1 from
MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
Then, we extract photometry using fixed circular apertures of varying sizes
centered on the mean position of the brightest star (on average) in each
frame.
The centroids and initial flux estimates were measured using
\project{simplexy}, a component of the \project{Astrometry.net} pipeline
\citep{astrometry}.
For each time series, we used 20 circular apertures ranging in radius from 0.5
to 10 pixels and---following \citet{vanderberg-a}---chose the aperture size
that resulted in the smallest CDPP \dfmtodo{CITE CDPP-Jessie Christiansen,
Jon Jenkins, et al 2012} with a 6 hour
window.\footnote{Note that although we chose a specific aperture, photometry
for every aperture size is available online at \dfmtodo{some URL}.}

Most methods for analyzing \KT\ data---and \kepler\ data, for that
matter---involves some sort of pre-processing or ``de-trending'' step.
For example, \citet{vanderberg-a} measure the centroid motion for each star
and regress out any signal in their aperture photometry that can be fit by
this motion.
Similarly, \citet{crossfield} iteratively construct a robust Gaussian Process
model for the photometry as a function of the measured centroids and de-trend
using the mean prediction from that model.
In our analysis, we don't do any further preprocessing of the light curves
because, as we describe in the next section, we simultaneously fit for the
trends and the transit signals that we are searching for.

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends caused by pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the detector.
To exploit this fact, the \project{PDC} component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``eigen-light curves'' (ELCs) found by
running Principal Component Analysis (PCA) on a set of light curves
\citep{map-pdc1, map-pdc2}.
Similarly, we ran PCA (as implemented by the \project{scikit-learn} project
\citealt{sklearn}) on the full set of Campaign 1 light curves to determine a
basis of representative ELCs.
We chose to use the top 150 components---many more than are normally
used---for our model described in the following section.
\Fig{pca} shows the top few ELCs.

>>>>

The methods developed within this paper are highly relevant to the upcoming
\tess\ mission (Cite-Ricker 14).
\tess will feature pointing precision of $\sim 3$ arcseconds (cite),
similar to the level of pointing drift with \KT.
Moreover, the typical star will be only observed for one month at a time, and
the typical transit detection will be at a similar signal-to-noise ratio as
with \KT.

@@

The starting point for analysis is the raw pixel data.
We download the full set of XXX target pixel files for \KT's Campaign 1 from
MAST\footnote{\url{https://archive.stsci.edu/k2/}}.
Then, we extract photometry using fixed circular apertures of varying sizes
centered on the predicted location of the target star based on the world
coordinate system.
For each time series, we used circular apertures ranging in radius from 0.5 to
5 pixels (in steps of 0.5 pixels) and---following \citet{vanderberg-a}---chose
the aperture size that resulted in the smallest CDPP \dfmtodo{CITE CDPP-Jessie
Christiansen, Jon Jenkins, et al 2012} with a 6 hour window.\footnote{Note
that although we chose a specific aperture, photometry for every aperture size
is available online at \dfmtodo{some URL}.}

Most methods for analyzing \KT\ data---and \kepler\ data, for that
matter---involve some sort of pre-processing or ``de-trending'' step.
For example, \citet{vanderberg-a} measure the centroid motion for each star
and regress out any signal in their aperture photometry that can be fit by
this motion.
Similarly, \citet{crossfield} iteratively construct a robust Gaussian Process
model for the photometry as a function of the measured centroids and de-trend
using the mean prediction from that model.
In our analysis, we don't do any further preprocessing of the light curves
because, as we describe in the next section, we simultaneously fit for the
trends and the transit signals that we are searching for.

One key realization that is also exploited by the official \kepler\ pipeline
is that the systematic trends caused by pointing shifts and other instrumental
effects are shared---with different signs and weights---by all the stars on
the detector.
To make use of this, the \project{PDC} component of the \kepler\ pipeline
removes any trends from the light curves that can be fit using a linear
combination of a small number of ``eigen-light curves'' (ELCs) found by
running Principal Component Analysis (PCA) on a set of light curves
\citep{map-pdc1, map-pdc2}.
Similarly, we ran PCA on the full set of Campaign 1 light curves to determine
a basis of representative ELCs.
We chose to use the top 150 components---many more than are normally
used---for our model described in the following section.
\Fig{pca} shows the top few ELCs.
